Manuscript

### 2015-02-04 inst/simulation/manuscript.Rmd
...

# Mean encounter rates
aggrates <- data.frame()
for (scenario in allScenarios) {
  study <- getMSS(scenario=scenario)$study

@@

  y <- ddply(rates, .(year), function(x, scenario) data.frame(scenario=scenario, rate.mean=mean(x$rate), rate.sd=sd(x$rate)), scenario=scenario)
  aggrates <- rbind(aggrates, y)
}

subset(aggrates, year==2001)
```

@@

@@

dir <- normalizePath(context$figuresDirectory)
table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1), file=file.path(dir, "table-1a.csv"))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1), file=file.path(dir, "table-1b.csv"))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp;

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1), file=file.path(dir, "table-1c.csv"))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp;

write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```

>>>>

# Mean encounter rates
#aggrates <- data.frame()
aggrates <- ldply(allScenarios, function(scenario) {
  study <- getMSS(scenario=scenario)$study

@@

  y <- ddply(rates, .(year), function(x, scenario) data.frame(scenario=scenario, rate.mean=mean(x$rate), rate.sd=sd(x$rate)), scenario=scenario)
  #aggrates <- rbind(aggrates, y)
  return(y)
}, .parallel=T)

subset(aggrates, year==2020)
```

@@

```{r figure-3-init-2-test, eval=FALSE}
populationSizes <- getPopulationSizes(scenarios=scenarios[1:4], modelNames=modelNames[3:4])
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios[1:4], "combined"), modelNames=modelNames[3:4])
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios[1:4], "10days"), modelNames=modelNames[3:4])
```

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

table2 <- getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, overEstimate=20000)
logTable2 <- getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, overEstimate=log10(20000+1))
logTable2$MeanProp <- table2$MeanProp; logTable2$SDProp <- table2$SDProp;

table3 <- getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, overEstimate=2000)
logTable3 <- getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, overEstimate=log10(2000+1))
logTable3$MeanProp <- table3$MeanProp; logTable3$SDProp <- table3$SDProp;

dir <- normalizePath(context$figuresDirectory)
write.csv(logTable1, file=file.path(dir, "table-1a.csv"))
write.csv(logTable2, file=file.path(dir, "table-2a.csv"))
write.csv(logTable3, file=file.path(dir, "table-3a.csv"))
```
